### 2023-08-18 2.State/lstm.tex
Worked on lstm state in train

\subsubsection{\acf{CIFG} \ac{LSTM} or \acf{GRU}}
The \ac{CIFG} \ac{LSTM} or more commonly known as \ac{GRU}. \cite{gru,gruKeras,gruPyTorch}

>>>>

\subsubsection{\acf{CIFG} \ac{LSTM} or \acf{GRU}}
The \ac{CIFG} \ac{LSTM} or more commonly known as \ac{GRU}. \cite{gru,gruKeras,gruPyTorch} As it's name implies, \acl{CIFG}, links the input and forget gates as such, $f_t=1-i_t$. Other differences are :
\begin{itemize}
  \item No peepholes and output activation function.
  \item Combined hidden state and cell state.
  \item The candidate cell state is point wise multiplied with the output gate before the activation function.
\end{itemize}

This is clearer with the math equations :
\begin{equation}\label{eq:cellGGRU}
  \tilde{c}_t = tanh(w_{cx}\cdot x_t + w_{ch}\cdot(o_t \odot h_{t-1}) + b_c)
\end{equation}
\begin{equation}\label{eq:hiddenGRU}
  h_t=(1-i_t)\cdot h_{t-1} + i_t \cdot \tilde{c}_t
\end{equation}
